Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-16 paper.tex

To estimate the uncertainty on fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics 199
different simulations.  For each deployed facility, the
parameters are normally distributed with an artificially large standard
deviation of $10\%$.

To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models} were
updated\cite{mouginot_2018, cyclass} to evaluate uncertainty of several
operational parameters in their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
facilities of Cycamore and CyCLASS.

@@

@@

\subsection{The Fuel Cycle Scenario}
This work aims to assess the impact of the operational uncertainties of a simple
transition, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. As shown in Figure \ref{fig:cycle}, this is a
transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with the full production,
        the \glspl{LWR} contribution, the \glspl{FBR} labelled in blue, orange, and green, respectively.}
    \label{fig:power}
\end{figure}

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed material availability).  The enrichment of the \gls{UOX} is processed
on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) is present
between all facilities with constant processing rates.

It must be noted that for this work, the fuel enrichment was determined by a
fuel fabrication model\cite{Leniau2015125} which
calculates the fissile fraction required in the fuel to reach a target
burnup at the end of irradiation.  In this study, the uncertainty on the fuel
enrichment is not applied directly on the effective enrichment but on the target
parameter (the burnup), which leads to a fuel enrichment uncertainty close to
$10\%$.

@@

As nuclear archaeology main interests are high enrich uranium production and
fissile inventories, this specific study will mainly focus on the uncertainty on
the total quantity of natural uranium used and on the total unused fissile
inventory (unused reprocessed plutonium).

Generated power will briefly being investigated to ensure the overall
uncertainty study will not be contaminated with fuel miss loading, which could
be interesting but are not the focus on this work.

For this study 6 set of 199 simulations, and a reference calculation have been
computed: One for each of the 5 uncertain parameters,Tab.
\ref{tab:package_uncertainty}  (separation efficiency, residence time, UOX fuel
enrichment, reactor cycle length, reactor thermal power), one varying parameter
the 4 others remaining fix, one with all 5 parameters varying and one single
simulation where all the 5 parameters were fixed at the mean value.

In the following, each total uncertainty is reported at $\pm1\sigma$ around the
mean values of the corresponding uncertainty set at each time step.  The time
dependant relative uncertainties are computed as the standard deviation of a
single set over its mean value at the corresponding time.

>>>>

To estimate the uncertainty of fuel cycle output metrics, a Total Monte
Carlo approach has been applied.  In the following, output metric uncertainty
corresponds to the standard deviation of the output metrics from 199
different simulations.  For each deployed facility, the
parameters are normally distributed with an artificially large standard
deviation of $10\%$.

To pursue this work, both the Cycamore\cite{cycamore} package\footnote{Low
fidelity facilities package for Cyclus} and the
CyCLASS\footnote{Reactor and fuel fabrication facility based on CLASS\cite{CLASS} models} were
updated\cite{mouginot_2018, cyclass} to evaluate the uncertainty of several
operational parameters in their associated facilities.  Table
\ref{tab:package_uncertainty} summarizes all uncertainty-tracking modifications implemented in the
facilities of Cycamore and CyCLASS.

@@

\subsection{The Fuel Cycle Scenario}
This work aims to assess the impact of the operational uncertainties of a simple
transition, inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}. Pictured in Figure \ref{fig:cycle}, this is a
transition from a light water reactor fleet loaded with \gls{UOX} fuel to a
sodium fast reactor fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the generated power (Figure \ref{fig:power}).
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Illustration of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.18]{power.png}
    \caption{Electric power generated over time, with the full production,
        the \gls{LWR} contribution, and the \gls{FBR} contribution labeled in blue, orange, and green, respectively.}
    \label{fig:power}
\end{figure}

Both fuel reprocessing and fabrication are done at a constant rate (constrained
by the feed material availability).  The enrichment of the \gls{UOX} is processed
on demand.  Buffer storages (not shown in Figure \ref{fig:cycle}) are present
between all facilities with constant processing rates.

@@

@@

The main interests of nuclear archaeology involve highly enriched uranium production and
fissile inventories, so this study mainly focuses on the uncertainties of
the total quantity of natural uranium used and the total unused fissile
inventory (unused reprocessed plutonium).  
Generated power is also briefly being investigated to ensure the overall
uncertainty is not contaminated with a missed fuel loading, which could
be interesting but is not the focus of this work.

For this study, the 199 simulations were performed six times, and a reference calculation was also
computed. With the five parameters in Table
\ref{tab:package_uncertainty} (separation efficiency, residence time, \gls{UOX} fuel
enrichment, reactor cycle length, reactor thermal power) being tracked, the six sets are divided as follows: five sets where a single parameter is varied and 
the four others remain fixed, and one with all five parameters being varied. 
The reference calculation is a single
simulation with all five parameters fixed at the mean value.

In the following, each total uncertainty is reported at $\pm1\sigma$ around the
mean values of the corresponding uncertainty set at each time step.  The 
time-dependant relative uncertainties are computed as the standard deviation of a
single set over its mean value at the corresponding time.
